### 2023-11-15 related.tex
Updates from Overleaf

For systems rooted in constraint solving, there has been considerable work in improving error localization because it is notoriously well-understood that such systems make error localization difficult, and programmers are often confused by localization decisions \cite{wand1986} because they are rooted in \emph{ad hoc} traversal orders \cite{mcadam1999,lee1998}. More recently, there has been a series of papers on finding the most likely location for an error based on either manual weights \cite{zhang2014,pavlinovic2014} or learned weights \cite{seidel2017}.
While improving the situation somewhat, these remain fundamentally \emph{ad hoc} in their need to guess intent. However, data-driven approaches could perhaps be layered atop type hole inference to improve the ranking or filtering of suggestions.

>>>>

For systems rooted in constraint solving, there has been considerable work in improving error localization because such systems are notorious for making error localization difficult, and programmers are often confused by localization decisions \cite{wand1986} because they are rooted in \emph{ad hoc} traversal orders \cite{mcadam1999,lee1998}. 
More recently, there has been a series of papers that discuss finding the most likely location for an error based on maximum likelihood estimation \cite{zhang2014} or manual/learned weights \cite{pavlinovic2014,seidel2017}.
While improving the situation somewhat, these remain fundamentally \emph{ad hoc} in their need to guess intent. However, data-driven approaches could perhaps be layered atop type hole inference to improve the ranking or filtering of suggestions.
